### 2012-12-27 inst/examples/allee.Rmd
Large noise case handled correctly by using GP's parametric form for the noise (Gaussian vs lognormal)

```{r gp-priors}
s2.p <- c(50,50)  # inverse gamma mean is 
tau2.p <- c(20,1)
d.p = c(10, 1/0.01, 10, 1/0.01)
nug.p = c(10, 1/0.01, 10, 1/0.01) # gamma mean
s2_prior <- function(x) dinvgamma(x, s2.p[1], s2.p[2])
tau2_prior <- function(x) dinvgamma(x, tau2.p[1], tau2.p[2])
d_prior <- function(x) dgamma(x, d.p[1], scale = d.p[2]) + dgamma(x, d.p[3], scale = d.p[4])
nug_prior <- function(x) dgamma(x, nug.p[1], scale = nug.p[2]) + dgamma(x, nug.p[3], scale = nug.p[4])
beta0_prior <- function(x, tau) dnorm(x, 0, tau)
beta = c(0)
priors <- list(s2 = s2_prior, tau2 = tau2_prior, beta0 = dnorm, nug = nug_prior, d = d_prior, ldetK = function(x) 0)
```

@@

```{r sdp-pars-explore}
sigma_g <- 0.05
sigma_m <- 0.0
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

@@

```{r}
  obs <- sim_obs(Xo, z_g, f, p, Tobs=35, nz=1, 
                 harvest = sort(rep(seq(0, .7, length=7), 5)), seed = seed_i)
```

```{r}
  alt <- par_est(obs)
  est <- par_est_allee(obs, f, p)
```

>>>>

```{r gp-priors}
#inv gamma has mean b / (a - 1) (assuming a>1) and variance b ^ 2 / ((a - 2) * (a - 1) ^ 2) (assuming a>2)
s2.p <- c(50,50)  # inverse gamma mean is 
tau2.p <- c(20,1)
d.p = c(10, 1/0.01, 10, 1/0.01)
nug.p = c(10, 1/0.1, 10, 1/0.1) # gamma mean
s2_prior <- function(x) dinvgamma(x, s2.p[1], s2.p[2])
tau2_prior <- function(x) dinvgamma(x, tau2.p[1], tau2.p[2])
d_prior <- function(x) dgamma(x, d.p[1], scale = d.p[2]) + dgamma(x, d.p[3], scale = d.p[4])
nug_prior <- function(x) dgamma(x, nug.p[1], scale = nug.p[2]) + dgamma(x, nug.p[3], scale = nug.p[4])
beta0_prior <- function(x, tau) dnorm(x, 0, tau)
beta = c(0)
priors <- list(s2 = s2_prior, tau2 = tau2_prior, beta0 = dnorm, nug = nug_prior, d = d_prior, ldetK = function(x) 0)
```

@@

```{r sdp-pars-explore}
sigma_g <- 0.1
sigma_m <- 0.0
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

@@

```{r}
  obs <- sim_obs(Xo, z_g, f, p, Tobs=35, nz=15, 
                 harvest = sort(rep(seq(0, .5, length=7), 5)), seed = seed_i)
```

```{r}
  alt <- par_est(obs,  init = c(r=1.5, K=mean(obs$x), s=1))
  est <- par_est_allee(obs, f, p,  init = c(p[1]+1, p[2]-1, p[3]-2, 
                                   s = sigma_g + abs(rnorm(1,0,.1))))
```
